---
title: "Report Title"
author: "Kevin Donkers (EI CDT) - 700063874"
date: "01/01/2021"
output:
  bookdown::html_document2:
    fig_caption: yes
    number_sections: false
    smart: no
  bookdown::pdf_document2:
    fig_caption: yes
    number_sections: false
    toc: false
---
```{r setup, include=FALSE}
library(here)
library(bookdown)
library(kableExtra)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, cache=TRUE, warning=FALSE, include=FALSE)
knitr::read_chunk(here::here('scripts/init.R'))
knitr::read_chunk(here::here('scripts/section1.R'))
```

# 0. Setup

Code for loading and wrangling data:
```{r 0LoadData, include=TRUE, echo=TRUE}
```

\pagebreak
# 1. First section

**Referencing objects:**
Make sure to use CamelCase for reference tags - special characters break the referencing logic.


Initialised library imports, etc. in this section of the code.
Hide output.

```{r 1Init}
```


Include the output of some code here.
Hide code, show output.

```{r 1Result, include=TRUE}
```


Include code and it's the output here.
Show code and output.

```{r 1Code, include=TRUE, echo=TRUE}
```


Include a table here, which has been formatted using `knitr::kable` and `kableExtra::kable_styling`.

Captions need to be set when calling `knitr::kable`.

Reference the table like this -> Table \@ref(tab:1Table)

```{r 1Table, include=TRUE}
```


Include a plot without code.

Set the plot parameters (e.g. `fig.height`, `fig.cap`) at this level.

Reference figure like this -> Figure \@ref(fig:1Plot)

```{r 1Plot, include=TRUE, fig.height=2, fig.cap="This is a figure."}
```

